---
title: "Checks report for Ros import"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)"
output:
  html_document:
    css: "./templates/html_template.css"
    includes:
      in_header: "./templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---

# Concepts

**TODO**

## Models

We use the Model-driven development (MDD) concept.

We define a model in `json` format for each fishery domain and for each version of the model.

In the directory `models` you find the models.

A model is a mapping for each column of the xlsx file to import and map it the corresponding column of the database. We also add some behaviors and actions to do when the column is imported.

From this model we generate a `R` file to be able to do the import.

## Set up our database connection
```{r}
# Set up our database connection (if necessary)
# address of the host
# Sys.setenv(IOTC_ROS_DB_HOST="xxx")
# db name
# Sys.setenv(IOTC_ROS_DB_NAME=IOTC_ROS)
# db port
# Sys.setenv(IOTC_ROS_DB_PORT=5432)
# db user name
# Sys.setenv(IOTC_ROS_DB_USER="xxx")
# db user password
# Sys.setenv(IOTC_ROS_DB_PWD="a")
Sys.setenv(IOTC_ROS_DB_USER = "ros-admin", IOTC_ROS_DB_PWD = "a")
```
## Load sources

```{r, warning = FALSE}
source("R/00_mappings.R")
source("R/00_ros_database.R")
source("./R/01_check_structure.R")
source("R/02_check_data.R")
source("R/03_generate_report.R")
```
## Load models
```{r}

ros_ll_import_models <- load_models("LL", "3.3.0", "./models")
ros_ps_import_models <- load_models("PS", "3.3.0", "./models")
```

## Check one ll input
```{r}
check_ll_one_result <- check_one(connect_to_ros,
                                 ros_ll_import_models,
                                 "../iotc-ros-input-data/data/LL",
                                 "../iotc-ros-input-data/report/LL",
                                 "../iotc-ros-input-data/data/LL/2022/EU-FRANCE/ROS_LL_data_reporting_EU.FRA.REU_2022.xlsx",
                                 "test")
```

## Check all ll inputs
```{r}
check_ll_all_result <- check_all(connect_to_ros,
                                 ros_ll_import_models,
                                 "../iotc-ros-input-data/data/LL",
                                 "../iotc-ros-input-data/report/LL",
                                 timestamp = "test")
```
## Check one ps input
```{r}
check_ps_one_result <- check_one(connect_to_ros,
                                 ros_ps_import_models,
                                 "../iotc-ros-input-data/data/PS",
                                 "../iotc-ros-input-data/report/PS",
                                 "../iotc-ros-input-data/data/PS/2023/EU-ITALY/ROS_PS_data_reporting_EU.ITA_2023.xlsx",
                                 "test")
```
## Check all ps inputs
```{r}
check_ps_all_result <- check_all(connect_to_ros,
                                 ros_ps_import_models,
                                 "../iotc-ros-input-data/data/PS",
                                 "../iotc-ros-input-data/report/PS",
                                 timestamp = "test")

```