---
title: "Howto use importer"
output: html_notebook
---

# Concepts

## Object model

We use the `R6` package to define some classes (as if you were using Java).

## Models

We use the Model-driven development (MDD) concept.

We define a model in `json` format for each fishery domain and for each version of the model.

In the directory `models` you find the models.

A model is a mapping for each column of the xlsx file to import and map it the corresponding column of the database. We also add some behaviors and actions to do when the column is imported.

From this model we generate a `R` file to be able to do the import.

## Importers

For each domain and version of the model we have an importer.

An importer is the entry point to import the data.

# Workflow to use an importer

We describe here the workflow to use an importer.

## Connections to the database(s) (required)

This first step is to define the connection to the database(s).

You have to load the [iotc_db_connections.R](./R/iotc_db_connections.R) file.

Then set your credentials, says first define the server, then database credentials.

```{r}
source("../iotc-registries/ros/utils.R")
# Load the R file
source("./R/db_connections.R")
# Set the server
set_default_db_server(SERVER_CACHE, "localhost")
# Set credentials for IOTC_ROS databse
set_credentials_for_db(CREDENTIALS_CACHE, IOTC_ROS, "ros-admin", "a")
# Set credentials for IOTC_Reference_Data databse (this is optional)
set_credentials_for_db(CREDENTIALS_CACHE, IOTC_REFERENCE_DATA, "ros-admin", "a")
source("./R/db_utils.R")
source("./R/db_classes.R")
source("./R/checks.R")
source("./R/mappings.R")
source("./R/input_file.R")
source("./R/import_context.R")
source("./R/import_utils.R")
```

## Load models (required)

```{r}

ros_import_models <- load_models("LL", "3.3.0", "./models")

```

## Check one input (optional)

```{r}
check_one(DB_IOTC_ROS, ros_import_models, "../iotc-ros-input-data/data/LL/2022/EU-FRANCE/ROS_LL_data_reporting_EU.FRA.REU_2022.xlsx")
```

## Check alls input (optional)

```{r}

check_all(DB_IOTC_ROS,
          ros_import_models,
          "../iotc-ros-input-data/data/LL",
"test")

```